What really matters (and to whom): Investigating heterogeneous effects in high-dimensional conjoint analyses

### 2024-12-18 Manuscript files/Manuscript.qmd
changes to manuscript

col_header2 <- textGrob("Large Model", x=0.5, hjust=0.5, gp=gpar(fontface="bold", fontsize=10))
col_subheader2 <- textGrob("Burn-In: 1000 \nPosterior Draws: 5000", x=0.5, hjust=0.5, gp=gpar(fontsize=8))

@@

# Define column headers (centered)
col_header1 <- textGrob("Attribute 1\nUkrainian Military Casualties", x=0.5, hjust=0.5, gp=gpar(fontface="bold", fontsize=10))
col_subheader1 <- textGrob("Large Model\nBurn-In: 100 \nPosterior Draws: 1000", x=0.5, hjust=0.5, gp=gpar(fontsize=8))

col_header2 <- textGrob("Attribute 9\nSovereignity", x=0.5, hjust=0.5, gp=gpar(fontface="bold", fontsize=10))
col_subheader2 <- textGrob("Large Model\nBurn-In: 100 \nPosterior Draws: 1000", x=0.5, hjust=0.5, gp=gpar(fontsize=8))

>>>>

col_header2 <- textGrob("Large Model", x=0.5, hjust=0.5, gp=gpar(fontface="bold", fontsize=10))
col_subheader2 <- textGrob("Burn-In: 2000 \nPosterior Draws: 5000", x=0.5, hjust=0.5, gp=gpar(fontsize=8))

@@

# Define column headers (centered)
col_header1 <- textGrob("Attribute 1\nUkrainian Military Casualties", x=0.5, hjust=0.5, gp=gpar(fontface="bold", fontsize=10))
col_subheader1 <- textGrob("Large Model\nBurn-In: 2000 \nPosterior Draws: 5000", x=0.5, hjust=0.5, gp=gpar(fontsize=8))

col_header2 <- textGrob("Attribute 9\nSovereignity", x=0.5, hjust=0.5, gp=gpar(fontface="bold", fontsize=10))
col_subheader2 <- textGrob("Large Model\nBurn-In: 2000 \nPosterior Draws: 5000", x=0.5, hjust=0.5, gp=gpar(fontsize=8))
